Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-12 doc/report/msc-report.tex
doc/report/msc-report.tex: added end of itemize in glossary.

\begin{itemize}
\item \texttt{Serializing}

Serializing data is the task of converting an object into a sequence of
bits so that it can be stored on a storage medium or transmitted over a
network link. Rereading the sequence of bits should restore the original
state of the object it was in before the serialization.

>>>>

\begin{itemize}
\item \texttt{Serializing}
Serializing data is the task of converting an object into a sequence of
bits so that it can be stored on a storage medium or transmitted over a
network link. Rereading the sequence of bits should restore the original
state of the object it was in before the serialization.
\end{itemize}
